\huge A Better (One-Line!) Title Here

### 2016-10-20 pets2017-paper/pets2017-paper.tex
add setup section for first user test too (the second had it..)
minor tweaks at first user test's recruitment wording.

We recruited our users from Craigslist, vaguely asking to evaluate a piece of software. 
The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
SurveyGizmo online survey that collected their demographics, technical expertise, and familiarity with Tor.
The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
We selected participants in each censorship environment to have at least one person who has never heard of Tor, 
at least one person who has only heard of Tor, and exactly one person who has previously used Tor. We tried to evenly distribute any participants who had technical
expertise or used particular security tools throughout the censorship environments.

Of our 16 participants, 53.3\% were male. 
Ages ranged from 20 to~62 years
($\mu = 24.5$, $\sigma = 12.6$). 
93.3\% of our participants had at least
a college education.
4 had used Tor before;
5 had heard of Tor but not used it;
and the remaining 8 had never heard nor used it.

>>>>

We recruited users from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}. 
The recruitment posting linked an online survey that collected their demographics, technical expertise, and familiarity with Tor.

Of our 16 participants, 53.3\% were male. 
Ages ranged from 20 to~62 years
($\mu = 24.5$, $\sigma = 12.6$). 
93.3\% of our participants had at least
a college education.
4 had used Tor before;
5 had heard of Tor but not used it;
and the remaining 8 had never heard nor used it. 
We distributed participants so that each experimental condition had at least one person who has never heard of Tor, at least one person who has only heard of Tor, and one person who has previously used Tor. The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.
}

\subsection{Setup} 
{\color {blue}
Setup details here.
}
